manuscript_notes

### 2024-10-24 notes/manuscript_notes.Rmd
update notes todo

>>>>

# 23 oktober 2024

Still to do:
- combine tables showing person-trial and person-trial-period data sets
- REF for regression (line 145) 
- update section 3 and add REFs (line 200-215)

- REF for time-to-death (line 127 in ms.) : Done
- REF for reviews and tutorials on EHA (line 140) : Done
- change paragraph (delete it and refer to suppl. material?), and add error bars to Figure 2? (line 162): Done (no error bars added, but I refer to suppl. material)
- REF sampling bias (line 332): Instead of adding a REF, I rephrased the sentence.
- REF for package MASS (line 665) : Done
- REF for prevalence (line 710) : Done
-frequentist versus Bayesian plot with intervals: Done
- summary of steps involved in tutorials: Done.
- check odds ratio rounding : Done 
(added to apa_table(): format.args = list(
       digits = c(0, 2,2,2,2,2,5),
        decimal.mark = ".", big.mark = ""))
